ICNV-TV: A read-depth based Copy Number Variation detection tool

### 2016-04-13 paper.tex
Update

%%%%%%% all the required packages are loaded%%%%
\usepackage{filecontents}
\usepackage[style=ieee,backend=biber]{biblatex}
\usepackage{graphicx}
\usepackage{lmodern}	
\usepackage{enumerate}
\usepackage{float}

@@

\subsubsection{Postprocessing}
 This stage involves identifying regions with abnormal copy number and determining their absolute copy numbers. To do so determination of upper and lower thresholds is done. For generally thresholds as simple as 1.5X and 0.5X of the average RD value are used as upper and lower threshold respectively. We use a slightly less strength viz., 1.45X and 0.55X of the average RD value as upper and lower thresholds respectively.

\section{Results}
Discussion about what has been done
\subsection{Simulated Data}
\subsection{Real Data Analysis}
\subsection{Sub-population Analysis}
\begin{figure*}[h]
	\includegraphics[width=\textwidth]{final.jpg}
	\caption{This is a test image}
	\label{fig1: this is test image}
\end{figure*}

>>>>

%%%%%%% all the required packages are loaded%%%%
\usepackage{filecontents}
\usepackage[style=ieee,backend=biber]{biblatex}
\usepackage{graphicx}
\usepackage{lmodern}	
\usepackage{enumerate}
\usepackage{float}
\usepackage{multicol}
\usepackage{multirow}

@@

\subsubsection{Postprocessing}
 This stage involves identifying regions with abnormal copy number and determining their absolute copy numbers. For this the average RD value is taken as normal representing the copy number 2.To do so determination of upper and lower thresholds is done. For generally thresholds as simple as 1.5X and 0.5X of the average RD value are used as upper and lower threshold respectively. We use a slightly less strength viz., 1.45X and 0.55X of the average RD value as upper and lower thresholds respectively. The absolute copy number can be determining using the ratio of RD value of CNV region and average RD value.

\section{Results}
We have evaluated the proposed method on simulated data and population data from 1000 Genome Project. We use simulated data to compare proposed method with the other three CNV detection method. Our choice of method can be explained by the underlying segmentation process of each tool. ReadDepth uses Circular Binary Segmentation (CBS), while CNVnator uses Mean-shift algorithm and ControlFREEC uses ??. All of these methods do not require a control sample.

\subsection{Simulated Data}
A 10 Mbp segment of chromosome 4 of hg19 was taken as the starting sequencing. This very sequence is also used as the reference sequence. Now a total of 12 CNVs of different sizes (1000 bp, 2000 bp, 4000 bp) and copy number (1,3,4) were introduced to generate the sample sequence. Single-end reads were generated from the sample using ART simulator \cite{21} at different depths (10X-60X), each depth having 30 samples. Bowtie2 \cite{22} was used with default parameters for alignment to generate input alignment files in BAM format. Our method along with other three tools were tested on this data.We use a reciprocal overlap of 50\% to call a certain prediction as a true positive. Any prediction that doest not satisfy this condition is taken as a false positive. Below are the results in tabulated form for our method.
\begin{table*}[h]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
\textbf{Length (in bp)} & \textbf{Copy Number} & \textbf{10x} & \textbf{20x} & \textbf{30x} & \textbf{40x} & \textbf{50x} & \textbf{60x} \\ \hline
\multirow{3}{*}{987}    & 1                    & 2            & 11           & 19           & 26           & 22           & 21           \\ \cline{2-8} 
                        & 3                    & 2            & 9            & 18           & 15           & 15           & 17           \\ \cline{2-8} 
                        & 4                    & 30           & 30           & 30           & 30           & 30           & 30           \\ \hline
\multirow{3}{*}{2009}   & 1                    & 20           & 24           & 25           & 25           & 29           & 30           \\ \cline{2-8} 
                        & 3                    & 18           & 18           & 20           & 28           & 25           & 26           \\ \cline{2-8} 
                        & 4                    & 30           & 30           & 30           & 30           & 30           & 30           \\ \hline
\multirow{3}{*}{4024}   & 1                    & 27           & 29           & 29           & 30           & 30           & 30           \\ \cline{2-8} 
                        & 3                    & 23           & 27           & 28           & 30           & 30           & 30           \\ \cline{2-8} 
                        & 4                    & 30           & 30           & 30           & 30           & 30           & 30           \\ \hline
\multirow{3}{*}{4979}   & 1                    & 27           & 30           & 30           & 30           & 30           & 30           \\ \cline{2-8} 
                        & 3                    & 21           & 26           & 30           & 30           & 30           & 29           \\ \cline{2-8} 
                        & 4                    & 30           & 30           & 30           & 30           & 30           & 30           \\ \hline
FP                      & --                   & 0            & 0            & 0            & 0            & 0            & 0            \\ \hline
\end{tabular}
\end{table*}
\par We tested the others also on this simulated data and calculated the sensitivity and specificity values (Table II). Another important metric of a CNV detection is the prediction of breakpoints of the CNV regions. We calculated breakpoint error for samples at 30X and 60X for all the samples which can be found in table III.

\subsection{Population Study}
Populations of BEB, GIH, PJL, STU, ITU belonging to South Asian region were considered for the population analysis. For each population 10 samples of chromosome 11 were obtained from 1000 Genome Project, resulting in 50 samples for the study. We applied our method to detect CNVs. A bin size of 200 bp was used. Since, the data is of low coverage we considered all regions of the genome irrespective of its mappability. We then determined genes which fall in the reported CNVs. A total of 75  different genes where found to have an abnormal copy number across all the 50 samples.

\begin{figure*}[h]
	\includegraphics[width=\textwidth]{final.jpg}
	\caption{This is a test image}
	\label{fig1: this is test image}
\end{figure*}
